Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-19 prop_letter.tex
prop_letter.tex \paragraph{Gleason's Theorem} Updating...

In conventional quantum theory, when we measure a system described
by a state~$\ket{\phi}$ with respect to an observable~$\mathbf{O}$,
the probability of getting a eigenvalue~$\lambda$ is completely
determined by $\ket{\phi}$ and the eigenspace of $\lambda$, $S_{\lambda}$.
If we denote the projector to $S_{\lambda}$ as $P_{\lambda}$, the
probability of getting $\lambda$ can be computed by the Born rule~$\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\ip{\phi}{P_{\lambda}\phi}$.
In another word, any state~$\ket{\phi}$ defines a quantum probability
measure~$\mu_{\phi}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
where $\events$ is the set of all projectors in a Hilbert space.
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
which should satisfy:
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$. 
\end{itemize}
The Gleason's theorem asserts that there exists a unique mixed state~$\rho$
such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
$\Hilb$ of dimension $d\geq3$.

@@

>>>>

@@

In conventional quantum theory, when we measure a system described
by a density matrix~$\rho$ with respect to an observable~$\mathbf{O}$,
$\rho$ and the eigenspace of a eigenvalue~$\lambda$ completely
determines the probability of getting $\lambda$, which is computed
by the Born rule~$\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
where $P_{\lambda}$ denotes the projector to the eigenspace of $\lambda$.
In another word, any density matrix~$\rho$ defines a quantum probability
measure~$\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
where $\events$ is the set of all projectors in a Hilbert space.
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
which should satisfy:
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$. 
\end{itemize}
Gleason's theorem asserts that there exists a unique mixed state~$\rho$
such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
of dimension $d\geq3$.

\paragraph{Quantum Interval-valued Probability Measure (IVPM)}
